Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-19 paper.tex
edits to the intro

\todo[inline]{I see lots of mistakes regarding when to make words
  plural (whether they should have an ``s'' at the end). Please review
  the rules of English regarding plurals. The rules are tricky...
  some words don't have a plural form, like ``blame''. -JS
  \\---\\
  Will fix grammar after fixing all other problems -KC}
\todo[inline]{The first paragraph of the introduction should summarize
  the entire introduction, and in some sense, the entire paper. -JS
\\---\\
Fixed -KC}

@@

%Some readers might know that there are four blame strategies: $ \{Lazy, 
%Eager\} 
%\times \{D, UD\} $ \citep{siek2009exploring}. Eager strategies detect more 
%potential type errors, but 
%blame more programs. $ D $ and $ UD $ assign blame labels differently.
We focus on lazy strategies because recently \citet{new2019gradual} 
show that eager strategies are incompatible with $\eta$-equivalence of 
functions, which suggest that they are not very ideal. We are unaware of any 
strong argument favoring D or UD, so we study both \lazyD\ and \lazyUD.
\todo[inline]{Why do we need to explain why both LD and LUD? -KC
  \\---\\
Because the paper includes both. -JS
\\---\\
Fixed. -KC}

Here are our major contribution:
\begin{itemize}
	\item hypercoercion, a new space-efficient cast representation, which has a 
	structurally recursive composition and a more compact memory 	
	representation.
	\item a framework in Agda for proving correctness of cast represantations. 
	We conjecture that both coercion and threesome can fit into this framework.
	\item a formal proof that hypercoercion respects the semantics of cast 
	calculus
\end{itemize}

@@

\todo[inline]{Change the order of parameters for applyCast to take
	the value first and the cast second. -JS
	\\---\\
	Could you tell me why taking the value first is better?
	I am always taking the target of induction first. -KC
	\\---\\
    It's better because it matches the postfix syntax we are using for
    casts. Currently line 2 of applyCast for D is difficult to read,
    compare it with line 4 of applyCast for UD. -JS
    \\---\\
    Does it mean changing the syntax for casts to a prefix syntax would work as 
    well? 
    If yes, I prefer this way, because of the reason in my first response 
    and that function applications (apply) also takes arguments in this order.
    I have fixed it with my idea so that we can see if it works. This change is 
    easy to undo.
    -KC
    \\---\\
    Postfix is better than prefix because then the casts read left to right,
    which is the normal direction for English readers.
    Please make it so. BTW, the way you keep choosing notation etc.
    different from what I'm use to is making it more difficult than
    necessary for me to collaborate with you. If this keeps up,
    I may decide to stop. It's fine for you to ask why, it's not fine
    for you to choose to make things difficult for me. -JS
    \\---\\
    Sorry, I don't indent to make things difficult for you. I have turned to 
    postfix notation. -KC
    }

>>>>

\todo[inline]{I see lots of mistakes regarding when to make words
  plural (whether they should have an ``s'' at the end). Please review
  the rules of English regarding plurals. The rules are tricky...
  some words don't have a plural form, like ``blame''. -JS
  \\---\\
  Will fix grammar after fixing all other problems -KC}

@@

%Some readers might know that there are four blame strategies: $ \{Lazy, 
%Eager\} 
%\times \{D, UD\} $ \citep{siek2009exploring}. Eager strategies detect more 
%potential type errors, but 
%blame more programs. $ D $ and $ UD $ assign blame labels differently.

We focus on lazy cast strategies because we suspect that they are more
efficient that eager strategies, which is why lazy was chosen in the
Grift compiler \citep{Kuhlenschmidt:2019aa}, and because
\citet{new2019gradual} show that eager strategies are incompatible
with $\eta$-equivalence of functions. We are interested in the D blame
tracking strategy because it has a more straightforward notion safe
cast compared to UD \citep{siek2009exploring}, which is why D was
chosen Grift compiler. However, we are also intersted in UD because it
plays a prominent role in the gradual typing literature
\citep{wadler2009well}.

The primary contributions of this paper are:
\begin{itemize}
\item hypercoercions, a new space-efficient cast representation, which
  has a structurally recursive composition and a more compact memory
  representation.
\item a framework in Agda for proving correctness of cast
  represantations.  We conjecture that both coercion and
  threesome can fit into this framework.
\item a formal proof that hypercoercion respects the semantics
  of the \lazyD{} cast calculus.
\end{itemize}

@@
